Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-01-30 docs/msr.tex
more on the related work

Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
to detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach involved
the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern.

>>>>

Using {\it Micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
to detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach involved
the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern.

{\it Querying techniques} are used to answer a broad range of questions
regarding the evolution history of a project~\cite{HG05}. Bhattacharya et al.~\cite{BN11}
proposed a framework that is based upon recursively enumerable languages. The
framework can correlate software bugs with developers in various ways.
For instanse, return the list of bugs fixed by a specific developer.
Fischer et al.~\cite{FPG03} proposed an approach for
populating a release history database that combines code information
with bug tracking data. In this way, a developer can couple files that contain
common bugs, estimate code maturity with respect to the bugs and others.
